\DTLnewdb{researchquestions}

\newcommand{\RQadd}[7]{
    \DTLnewrow{researchquestions}
    \DTLnewdbentry{researchquestions}{id}{RQ-#1}
    \DTLnewdbentry{researchquestions}{label}{#2}
    \DTLnewdbentry{researchquestions}{short}{#3}
    \DTLnewdbentry{researchquestions}{long}{#4}
    \DTLnewdbentry{researchquestions}{method}{#5}
    \DTLnewdbentry{researchquestions}{tools}{#6}
    \DTLnewdbentry{researchquestions}{output}{#7}
}

\newcommand{\RQ}[2]{%
    \DTLfetch{researchquestions}{id}{#1}{#2}%
}

\newcommand{\RQtable}[1]{

    \begin{tabularx}{\textwidth}{l X}
        \toprule
        \textbf{#1}                & \textbf{\RQ{#1}{label}} \\
        \midrule
        % \textbf{Short Description } & \RQ{#1}{short}          \\
        \textbf{Description}       & \RQ{#1}{long}           \\
        \textbf{Research Method}   & \RQ{#1}{method}         \\
        \textbf{Instruments Tools} & \RQ{#1}{tools}          \\
        \textbf{Output Data}       & \RQ{#1}{output}         \\
        \bottomrule
    \end{tabularx}
}

\newcommand{\ResearchMatrix}{
    \DTLforeach{researchquestions}{
        \id=id%
    }{
        \RQtable{\id}
    }
}

\RQadd{1}{Requirements}
{What are the requirements?}
{What functional, performance, and safety requirements must the power generation and feed system meet to be integrated into the selected COTS drone?}
{Literature review and stakeholder analysis}
{Scientific literature, hydrogen and UAV standards, requirement templates}
{System requirements specification}

\RQadd{2}{Characteristics}
{How do the FCU and CGG work?}
{What are the relevant performance characteristics of Solid Flow’s cool gas generator and Stellar Space Industries’ flow control system?}
{Technical analysis and literature study}
{Supplier datasheets, technical documentation, prior test data}
{Performance characteristics overview}

\RQadd{3}{Flight-Time Improvement}
{What flight-time improvement is achievable?}
{What flight-time improvement is theoretically achievable with hydrogen storage and fuel cells compared to the drone’s current battery system?}
{Analytical modelling and comparison}
{Energy density calculations, MATLAB/Excel models}
{Theoretical flight-time estimation}

\RQadd{4}{System Architecture}
{Which system architecture is optimal?}
{Which system architecture best balances safety, efficiency, weight, system complexity, and manufacturability for the power generation and feed system?}
{Conceptual design and trade-off analysis}
{Morphological chart, decision matrix}
{Selected system architecture}

\RQadd{5}{Component Selection}
{Which components are most suitable?}
{Which components (fuel cell, intermediate electrical storage, power electronics) are most suitable based on the system requirements and design constraints?}
{Component selection study}
{Supplier datasheets, selection criteria tables}
{Selected component list with justification}

\RQadd{6}{Mechanical Integration}
{What mechanical modifications are required?}
{What mechanical modifications are required to integrate the hydrogen storage, generator, fuel cell, and power electronics into the drone airframe without compromising payload capacity?}
{Mechanical design}
{CAD software, mass and tolerance analysis}
{Mechanical design drawings and mass breakdown}

\RQadd{7}{Electrical Architecture}
{What electrical architecture ensures stable power delivery?}
{What electrical architecture ensures stable power delivery from the fuel cell system to the drone’s propulsion and onboard electronics?}
{Electrical system design}
{Electrical schematics, simulation tools}
{Electrical architecture and schematics}

\RQadd{8}{System Performance}
{How does the system perform during testing?}
{How does the integrated hydrogen-based power system perform during ground testing in terms of power output, stability, efficiency, and safety?}
{Experimental testing}
{Hydrogen supply, sensors, data acquisition system}
{Measured performance and test results}

\RQadd{9}{Feasibility and Risk}
{What risks affect system feasibility?}
{What technical risks, failure modes, or limitations affect the overall feasibility of implementing the system in operational drone flights?}
{Risk analysis and evaluation}
{FMEA, test observations, design review}
{Feasibility assessment and risk overview}
