\section{Scope}
% Exactly what is included and excluded from the project scope

% Describe activities on the border and wether they are included or excluded
% Begin and end dates
% Maximum budget
% Required resources (randvoorwaarden)

% From original project assignment:
% Designing a system overview of the complete power generation and feed system.
% Selecting components for the hydrogen fuel cell, intermediate electrical storage, and drone interfaces.
% Developing the electrical design of the power generation and feed system (fuel cells, intermediate storage, and connection to the COTS drone).
% Implementing mechanical modifications to the COTS drone to ensure system compatibility.
% Performing assembly and integration of the power generation and feed system into the drone.
% Conducting ground testing of the power generation and feed system using a gaseous hydrogen source.
% Compiling a comprehensive report of all findings and results.

% Is defining the mission scenario part of the project scope?
% Maybe adapt COTS drone to test bench or even custom drone. Would be nice if we can specify that already.

\textit{
    Describe activities on the border and wether they are included or excluded
    Begin and end dates
    Maximum budget
    Required resources (randvoorwaarden)
}

Activities that \emph{are} included (from original project assignment):
\begin{itemize}
    \item Designing a system overview of the complete power generation and feed system.
    \item Selecting components for the hydrogen fuel cell, intermediate electrical storage, and drone interfaces.
    \item Developing the electrical design of the power generation and feed system (fuel cells, intermediate storage, and connection to the COTS drone).
    \item Implementing mechanical modifications to the COTS drone to ensure system compatibility.
    \item Performing assembly and integration of the power generation and feed system into the drone.
    \item Conducting ground testing of the power generation and feed system using a gaseous hydrogen source.
    \item Compiling a comprehensive report of all findings and results.
\end{itemize}

\textit{
    Is defining the mission scenario part of the project scope?
    Maybe adapt COTS drone to test bench or even custom drone. Would be nice if we can specify that already.
    Add some activities that are explicitly excluded from the project scope?
}

\newpage
